Removing nonlinear batch effects using adversarial deep neural networks

### 2019-02-15 thesis.tex
Update captions

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mnist}
	\caption{\textbf{MNIST handwritten digits} (a) before any adjustment, (b), with artificial noise added, (c) adjusted for noise by ComBat, and (d) adjusted for noise by Confounded. Although Confounded seems to remove more noise from the background and make it look more like the original background, it struggles in some cases to accurately replicate the input data.}
	\label{fig:mnist}
\end{figure}\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/pca}
	\caption{\textbf{Principal components analysis} (PCA) of the GSE37199 dataset before and after batch adjustment with various adjusters.}
	\label{fig:pca}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/tsne}
	\caption{\textbf{T-distributed Stochastic Neighbor Embedding} (t-SNE) plot for the GSE37199 dataset before and after adjustment with several algorithms.}
	\label{fig:tsne}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mse}
	\caption{\textbf{Mean squared error} (MSE) between the data prior to and after adjustment with various algorithms.}
	\label{fig:mse}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mmd}
	\caption{\textbf{Maximum mean discrepancy} (MMD) between different batches. In cases with more than two batches, MMD is computed pairwise between each batch and averaged.}
	\label{fig:mmd}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/batch_accuracy}
	\caption{\textbf{Batch classification accuracy} Accuracies for batch classification for 4-fold cross validation repeated 10 times for several classifiers.}
	\label{fig:batch}
\end{figure}
\begin{table}
	\centering
	\csvautotabular{figures/rough/batch.csv}
	\caption{Batch classification accuracy}
	\label{tab:batch}
\end{table}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/true_class_accuracy}
	\caption{\textbf{True class classification accuracy} for several datasets and adjusters.}
	\label{fig:true_class}
\end{figure}
\begin{table}
	\centering
	\csvautotabular{figures/rough/true_class.csv}
	\caption{True class classification accuracies}
	\label{tab:true_class}
\end{table}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mnist}
	\caption{\textbf{MNIST handwritten digits} (a) before any adjustment, (b), with artificial noise added, (c) adjusted for noise by ComBat, and (d) adjusted for noise by Confounded. Although Confounded seems to remove more noise from the background and make it look more like the original background, it struggles in some cases to accurately replicate the input data.}
	\label{fig:mnist}
\end{figure}\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/pca}
	\caption{\textbf{Principal components analysis} (PCA) of the GSE37199 dataset before and after batch adjustment with various adjusters.}
	\label{fig:pca}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/tsne}
	\caption{\textbf{T-distributed Stochastic Neighbor Embedding} (t-SNE) plot for the GSE37199 dataset before and after adjustment with several algorithms.}
	\label{fig:tsne}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mse}
	\caption{\textbf{Mean squared error} (MSE) between the data prior to and after adjustment with various algorithms.}
	\label{fig:mse}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/mmd}
	\caption{\textbf{Maximum mean discrepancy} (MMD) between different batches. In cases with more than two batches, MMD is computed pairwise between each batch and averaged.}
	\label{fig:mmd}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/batch_accuracy}
	\caption{\textbf{Batch classification accuracy} Accuracies for batch classification for 4-fold cross validation repeated 10 times for several classifiers. See also Table \ref{tab:batch}.}
	\label{fig:batch}
\end{figure}
\begin{table}
	\centering
	\csvautotabular{figures/rough/batch.csv}
	\caption{\textbf{Batch classification accuracy} for several datasets and adjusters. The ideal batch adjuster would completely remove all signal due to batch and would therefore \textit{decrease} batch classification accuracy to around the baseline for all classifiers. See also Figure \ref{fig:batch}.}
	\label{tab:batch}
\end{table}
\begin{figure}
	\centering
	\includegraphics[width=4.5in]{figures/rough/true_class_accuracy}
	\caption{\textbf{True class classification accuracy} for several datasets and adjusters with 4-fold cross validation repeated 10 times. See also Table \ref{tab:true_class}.}
	\label{fig:true_class}
\end{figure}
\begin{table}
	\centering
	\csvautotabular{figures/rough/true_class.csv}
	\caption{\textbf{True class classification accuracy} for several datasets and adjusters. After adjustment by the ideal batch adjuster, all true class signal should be preserved, and all classifiers should therefore have the same accuracy in predicting true class before and after adjustment. See also Figure \ref{fig:true_class}}
	\label{tab:true_class}
\end{table}
